---
title: "Starter Notebook"
author: "You, Scientist"
format: html
execute:
  keep-md: true
---

```{r setup, include = FALSE}
#Load in any packages you need
library(tidyverse)

#Read in any data

```

## Challenge 1 : Listing four nucleotides

```{r}
nucl_names <- c("A", "T", "G", "C")
nucl_names #nucl_names represents the names of the nucleotides. 

```

## Challenge 2 : Creating a random string of 15 nucleotides

```{r}
randGenome <- sample(nucl_names, size = 15, replace = TRUE)
paste(randGenome, collapse = "")



```

### Challenge 3: Generate a random genome which is 1500 nucleotides long dataset

```{r}
set.seed(215)
genomeLength <- 1500
randGenome <- sample(nucl_names, size = 1500, replace = TRUE)
paste(randGenome, collapse = "")




```

### Challenge 4: Generating random genome consisting of 100 nucleotides

```{r}
set.seed(215)
genomeLength <- 100
randGenome <- sample(nucl_names, size = 100, replace = TRUE)
table(randGenome)


```

### Challenge 5: Writing my own loop 

```{r}
mySum <- 0

for(i in 1:10){
  mySum <- mySum + i
  print(mySum)
}


```

### Challenge 6 : 

### Generating a random genome substring consisting of 10 nucleotides using sample(),paste() and loop

```{r}
nucleotides <- c("A", "C", "G", "T")
genomeLength <- 10

randGenome <- paste(
  sample(nucleotides, size = genomeLength, replace = TRUE),
                   collapse = "")
print(randGenome)




```

### Using for loop to print each nucleotides in my random sample

```{r}
for(i in 1:nchar(randGenome)){
  
    print(str_sub(randGenome, start = i, end = i))
  }

```

### Challenge 7 :  Counting the number of occurrences of Adenine (A) in randGenome.

```{r}
sum_A <- 0

for(i in 1:nchar(randGenome)){
  if(str_sub(randGenome, start = i, end = i) == "A")
    sum_A <- sum_A + 1
    {
    print(sum_A)
  }
}

```

### Challenge 8 : Counting the frequencies of each of the four individual nucleotides.

```{r}










```
